Variance reduction for Markov chains via martingale representations

### 2020-04-13 aap/Revision/vr-mcmc-revision-new-new.tex
update vr-mcmc-revision-new-new.tex

\def\rmd{\mathrm{d}}
\def\rme{\mathrm{e}}
\def\rset{\mathbb{R}}
\def\NtrainPath{T}
\def\TrainSet{\mathcal{D}}
\modulolinenumbers[5]
\newcommand{\proofendsign}{$\Box$}
\newtheorem{thm}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{cor}{Corollary}
\newtheorem{example}{Example}
\newenvironment{proof}{{\noindent \bf Proof }}
 {{\hspace*{\fill}\proofendsign\par\bigskip}}
\def\TV{\operatorname{TV}}
\newcommand{\jac}[1]{\operatorname{J} _{#1}}

@@

Let $f$ be a bounded Borel function and $(X^x_{p})_{p \in \nset_0}$ be a Markov chain generated by ULA with constant step size $\gamma \in (0,\gamma_0]$ where $\gamma_0= m/L^2$. 
Let $c_0>0$. Then, for all $n \in \nset$, $\gamma \in (0,\gamma_0]$ satisfying $n\gamma > c_0$   

@@

\PVar[\pi_n^N(f)]\lesssim \frac{V(x)}{n\gamma} \eqsp,

@@

where $\lesssim$ stands for inequality up to a constant not depending on $\gamma \in (0,\gamma_0]$ and $n \in \nset$.

@@

The bound in Lemma~\ref{lem:variance} is sharp and can not be improved even in the case of a normal distribution $\pi.$

@@

Then, it holds that for $q=0,\ldots,n-1,$ and all $x$

@@

A^2_{q,\mathbf{k}}(x)\leq C_K \rme^{\varkappa n\gamma^2}(1+V(x)),\quad 1\leq |\mathbf{k}|\leq K,

@@

\left(\frac{\gamma}{2}\right)^{|I|K-1}
(1+V(x))

@@

with some positive constants $\varkappa, C_K$ not depending on $n$ and  $\gamma.$  The sum in \eqref{eq:Aqk2} runs over all nonempty subsets $I$ of the set $\{1,\ldots,d\}$

@@

Under assumptions of Theorem~\ref{th:mr},

@@

\PVar\left(\pi_{K,n}^{N}(f)\right)\lesssim n^{-1} \gamma^{K-1}  e^{\varkappa n\gamma^2}
\eqsp,

@@

where $\lesssim$ stands for inequality up to a constant not depending  on $n,$ $N$ and $\gamma$.

@@

\right)\leq C_{K}\gamma^{-1}e^{\varkappa n\gamma^2}(1+V(x)),\quad q=0,\ldots,n-1,

@@

\right)\leq C\gamma^{-1}e^{\varkappa n\gamma^2}(1+V(x)),\quad q=1,\ldots,n,

@@

\begin{lem}
\label{lem:var_poincare}
Under assumptions of Theorem~\ref{th:mr}, it holds
$$
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]\le  \gamma^{-1} C e^{\varkappa n\gamma^2}(1+V(x)), \quad q=1,\ldots,n,
$$
where $C,\varkappa>0$ are constants that do not depend on $n$ and $\gamma.$
\end{lem}
\begin{proof}
The expression
$\sum_{p=1}^q \partial_{y_1}^K f(X_p^x)$
can be viewed as a deterministic function of
$x,Z_1,Z_{2},\ldots,Z_q$
$$
\sum_{p=1}^q  \partial_{y_1}^K f(X_p^x)
=F(x,Z_1,Z_{2},\ldots,Z_q).
$$
By the (conditional) Gaussian Poincar\'e inequality,
we have
$$
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]
\le\mathsf E_x\left[
\|\nabla_Z F(x,Z_1,Z_{2},\ldots,Z_q)\|^2
\right],
$$
where $\nabla_Z F=(\partial_{Z_1} F,\ldots,\partial_{Z_q} F)$,
and $\|\cdot\|$ denotes the Euclidean norm.
Notice that \(\partial_{Z_j} F=\sqrt{\gamma}\,\partial_{y_j} F\) and
hence
$$
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]\leq\gamma^2\sum_{j=1}^{q}\mathsf{E}\left[\left(\sum_{p=1}^{q}\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right)^{2}\right].
$$
It is straightforward to check that
$\partial_{y_j}\partial_{y_1}^K f(X_p^x)=0$
whenever $p<j$. Therefore, we get
\begin{equation}\label{eq:10062018a2}
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]\leq\gamma^2\sum_{j=1}^{q}\mathsf{E}\left[\left(\sum_{p=j}^{q}\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right)^{2}\right].
\end{equation}
Now fix $p$ and $j$, $p\ge j$, in $\{1,\ldots,q\}$.
By Fa\`a di Bruno's formula
\[
\partial_{y_{1}}^{K}f\left(X_{p}^x\right)=\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X_{p}^x)\prod_{k=1}^{K}\left(\frac{\partial_{y_{1}}^{k}X^x_{p}}{k!}\right)^{m_{k}},
\]
where the sum is taken over all $K$-tuples of nonnegative integers
$(m_1,\ldots,m_K)$ satisfying
$$
1\cdot m_{1}+2\cdot m_{2}+\ldots+K\cdot m_{K}=K.
$$
Then
\begin{eqnarray*}
\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)
&=&\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K}+1)}(X^x_{p})\left[\partial_{y_{j}}X^x_{p}\right]\prod_{k=1}^{K}\left(\frac{\partial_{y_{1}}^{k}X_{p}^x}{k!}\right)^{m_{k}} \\
&&+\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X^x_{p})
\sum_{s=1}^{K}\frac{m_{s}}{s!}
\left(\frac{\partial_{y_{1}}^{s}X^x_{p}}{s!}\right)^{m_{s}-1}
\\
&& \times\left[\partial_{y_{j}}\partial_{y_{1}}^{s}X^x_{p}\right]
\prod_{k\le K,\,k\neq s}\left(\frac{\partial_{y_{1}}^{k}X^x_{p}}{k!}\right)^{m_{k}}.
\end{eqnarray*}
Using the bounds of
Lemmas \ref{lem:06062018a2} and~\ref{lem:06062018a3},
we obtain
\begin{eqnarray}
\label{eq:part-part}
\left|\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right|
\leq A_{K}\prod_{k=2}^{p}\alpha_{k}
\end{eqnarray}
with a suitable constant $A_{K}$.
Substituting this in~\eqref{eq:10062018a2},
we proceed as follows
\begin{align*}
\mathsf{Var}_x\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]
&\le
\gamma^2 A_{K}^{2}\sum_{j=1}^{q}
\mathsf{E}\left(\sum_{p=j}^{q}\prod_{k=2}^{p}\alpha_{k}\right)^{2}
\\
&\le
\frac{\gamma^2 A_{K}^{2}}{(1-\gamma B_\mu)^2}
\mathsf{E}\sum_{j=1}^{q}
\left(\sum_{p=j+1}^{q+1}  \prod_{k=2}^{p} \alpha_{k}
\right)^{2}
\\
%&=
%\frac{A_{K}^{2}}{(1-\gamma_1 b_\mu)^2}
%\sum_{j=l}^{q} \gamma_{j}
%\prod_{k=l+1}^{j} \alpha_{k}^2
%\left(
%\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=j+1}^{p} \alpha_{k}
%\right)^{2}
%\\
&\le
\frac{\gamma^2 A_{K}^{2}}{(1-\gamma B_\mu)^3}
\mathsf{E}\sum_{j=1}^{q}
\prod_{k=1}^{j} \alpha_{k}
\left(\sum_{p=j+1}^{q+1}  \prod_{k=j+1}^{p} \alpha_{k}
\right)^{2}
\end{align*}

Now, from the H\"older inequality, we obtain (with $\|X\|_p = (\mathsf{E}X^p)^{\frac{1}{p}}$)
\begin{align*}
\mathsf{E}\left[\sum_{j=1}^{q}\prod_{k=l}^{j}\alpha_{k}\left( \sum_{p=j+1}^{q+1}\prod_{k=j+1}^{p}\alpha_{k}\right)^{2}\right] & \leq\sum_{j=1}^{q}\left\Vert \prod_{k=1}^{j}\alpha_{k}\right\Vert _{2}\left\Vert \sum_{p=j+1}^{q+1} \prod_{k=j+1}^{p}\alpha_{k}\right\Vert _{4}^{2}\\
 & \leq\sum_{j=1}^{q} \left\Vert \prod_{k=1}^{j}\alpha_{k}\right\Vert _{2}\left(\sum_{p=j+1}^{q+1}\left\Vert \prod_{k=j+1}^{p}\alpha_{k}\right\Vert _{4}\right)^{2}.
\end{align*}
Now using the fact that $\prod\limits_{k=j+1}^{p}\alpha_{k} \leq \exp\left(-\sum\limits_{k=j+1}^{p}\gamma\mu'(X_{k-1}^x)\right),$
we get
\[
\mathsf{E}\left[\sum_{j=1}^{q}\prod_{k=1}^{j}\alpha_{k}\left(\sum_{p=j+1}^{q+1}\prod_{k=j+1}^{p}\alpha_{k}\right)^{2}\right]\leq\sum_{j=1}^{q} \zeta^{1/2}_{1,j}(2) \left(\sum_{p=j+1}^{q+1} \zeta^{1/4}_{j+1,p}(4)\right)^{2},
\]
where we denote
\[
\zeta_{l,j}(u)=\mathsf{E}\left[e^{-u\gamma\sum_{k=l}^{j}\mu'(X^x_{k-1})}\right],\quad u>0.
\]
Note that $\mu^{\prime}(x)$ is bounded due  our assumptions and from Theorem~1 in \cite{delyon1999small} and Lemma~\ref{lem:v_ergodicity} in Appendix~\ref{sec:appendix} it follows that
\[
\mathsf{E}\left[e^{-u\gamma\left(\sum_{k=l}^{j}[\mu'(X^x_{k-1})-\pi_\gamma(\mu')]\right)}\right]\leq C_1e^{\varkappa n\gamma^2}(1+V(x)),\quad u\gamma\leq \gamma_0,
\]
for some constants $\gamma_0$ and $C_1,\varkappa>0$. Then we have
\[
\zeta_{l,j}(u)=\mathsf{E}\left[e^{-s\gamma\sum_{k=l}^{j}\mu'(X^x_{k-1})}\right]\leq  C_1 e^{\varkappa n\gamma^2}(1+V(x))e^{-s\gamma (j-l+1)\pi_\gamma(\mu')}.
\]
Furthermore, since $\mu\pi',\mu'\pi\in L^{1}(\mathbb{R})$ and $\pi^{\prime}(x) = -\frac{1}{2}\pi(x)\mu(x)$, we have
\[
\pi(\mu')=\int\mu'(x)\pi(x)\,dx=-\int\mu(x)\pi'(x)\,dx=\frac{1}{2}\int\mu^{2}(x)\pi(x)\,dx>0
\]
Note also that \(\pi_\gamma(\mu^{\prime}) \geq \pi_\gamma(\mu^{\prime}) - C_2\sqrt{\gamma}\)
yielding the bound
\[
\zeta_{l,j}(s) \leq  C_1e^{\varkappa n\gamma^2}(1+V(x))e^{-s\gamma(j-l+1)\alpha}
\]
where $ \alpha = \frac{1}{2}\int \mu^2(x)\pi(x)\,dx - C_1\sqrt{\gamma} > 0$ for sufficiently small $\gamma$. Hence we obtain
\begin{align*}
\sum_{p=j+1}^{q+1} \zeta^{1/4}_{j+1,p}(4) &\leq (C_1e^{\varkappa n\gamma^2}(1+V(x)))^{1/4}\sum_{p=j+1}^{q+1}e^{-\gamma(p-j)\alpha}
\\
&\leq  (C_1e^{\varkappa n\gamma^2}(1+V(x)))^{1/4}\frac{1}{1-e^{- \gamma\alpha}}
\end{align*}
and
\begin{align*}
\sum_{j=1}^{q} \zeta^{1/2}_{1,j}(2) \leq (C_1e^{\varkappa n\gamma^2}(1+V(x)))^{1/2}\sum_{j=0}^{q}e^{-\gamma j\alpha}
\\
\leq  (C_1e^{\varkappa n\gamma^2}(1+V(x)))^{1/2}\frac{ 1}{1-e^{- \gamma\alpha}}.
\end{align*}
Thus the final bound follows:
\begin{align*}
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X^x_{p}\right)\right] \leq \gamma^{-1} C_K e^{\varkappa n\gamma^2} (1+V(x))
\end{align*}
 with $C_K$  depending neither on $q$ nor on $\gamma$. The proof is completed.
\end{proof}

@@

\begin{lem}
\label{lem:drift}
 Assume that the potential $U(x), x \in \mathbb{R}^d$ satisfies conditions {\bf (H1)} and {\bf (H2)} and without loss of generality consider $\nabla U(0) = 0$. Then the kernel $Q_\gamma$ from \eqref{eq:ula_kernel} satisfies drift condition \eqref{eq:lyapunov} for any $0 < \gamma < \overline{\gamma} = \frac{m}{4L}$ with drift function $V(x) = 1 + \|x\|^2$,   $\lambda = \exp{\left(-\frac{m}{2}\right)}$, $C = \frac{25K_2^2}{8} + d + m$ with $K_2$ from \eqref{eq:H3}, $m$ from {\bf (H2)}.
\end{lem}

@@

\begin{lem}
\label{lem:v_ergodicity}
 Assume that the potential $U(x), x \in \mathbb{R}^d$ satisfies conditions {\bf (H1)} and {\bf (H2)}. Then for $0 < \gamma < \overline{\gamma}=\frac{m}{4L^2}$, for any $x \in X$ it holds
$$
d_V(\delta_xQ_{\gamma}^{1,n},\pi_\gamma) \leq C\rho^n\left(V(x) + \pi_\gamma(V)\right)
$$
with $V(x) = 1 + \|x\|^2$ and constants
$$
C = \left(1 + \exp{\left(-\frac{m\gamma}{2}\right)}\right)\left(1+\frac{\overline{b}}{(1-\varepsilon)(1-\exp{\left(-\frac{m\gamma}{2}\right)} - \frac{2b}{1+d})}\right);
$$

>>>>

\def\rmd{\mathrm{d}}
\def\rme{\mathrm{e}}
\def\rset{\mathbb{R}}
\def\NtrainPath{T}
\def\TrainSet{\mathcal{D}}
\modulolinenumbers[5]
\newcommand{\proofendsign}{$\Box$}
\newtheorem{thm}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{remark}[thm]{Remark}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{example}[thm]{Example}
\newenvironment{proof}{{\noindent \bf Proof }}
 {{\hspace*{\fill}\proofendsign\par\bigskip}}
\def\TV{\operatorname{TV}}
\newcommand{\jac}[1]{\operatorname{J} _{#1}}

@@

Let $f$ be a bounded Borel function and $(X^x_{p})_{p \in \nset_0}$ be a Markov chain generated by ULA with constant step size $\gamma$. 
Let $c_0>0$. Then, there exist $C < \infty$ and $\gamma_0 > 0$, such that for all $n \in \nset$, $\gamma \in (0,\gamma_0]$ satisfying $n\gamma > c_0$, and $x \in \rset^d$, 

@@

\PVar\left[\pi_n^N(f)\right]\leq C (n \gamma)^{-1} V(x) \eqsp.

@@

@@

The bound in Lemma~\ref{lem:variance} is sharp and cannot be improved even in the case of a normal distribution $\pi.$

@@

Then, there exist $\gamma_0 > 0$, $C_K < \infty$, and $\varkappa > 0$  such that, for all $\gamma \in (0,\gamma_0]$, $n \in \nset$, and $x \in \rset^d$,

@@

A^2_{q,\mathbf{k}}(x)\leq C_K \rme^{\varkappa n\gamma^2}\{1+V(x)\} \,,\quad 1\leq |\mathbf{k}|\leq K, \quad \text{for all  $q=0,\ldots,n-1,$}

@@

\left(\frac{\gamma}{2}\right)^{|I|K-1} \, \{1+V(x)\} \eqsp, 

@@

where the sum in \eqref{eq:Aqk2} runs over all nonempty subsets $I$ of the set $\{1,\ldots,d\}$.

@@

Under assumptions of Theorem~\ref{th:mr}, there exist $\gamma_0 > 0$, $\tilde{C} < \infty$ and $\varkappa > 0$ such that for all $n \in \nset$, $\gamma \in (0,\gamma_0]$, $n\in \nset$, and $x \in \rset^d$, 

@@

\PVar\left[\pi_{K,n}^{N}(f)\right] \leq \tilde{C}  n^{-1} \gamma^{K-1}  \rme^{\varkappa n\gamma^2}
\eqsp.

@@

@@

\right)\leq C_{K}\gamma^{-1}\rme^{\varkappa n\gamma^2}(1+V(x)),\quad q=0,\ldots,n-1,

@@

\right)\leq C\gamma^{-1} \rme^{\varkappa n\gamma^2}(1+V(x)),\quad q=1,\ldots,n,

@@

\begin{lem}
\label{lem:var_poincare}
Under assumptions of Theorem~\ref{th:mr}, it holds
$$
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]\le  \gamma^{-1} C \rme^{\varkappa n\gamma^2}(1+V(x)), \quad q=1,\ldots,n,
$$
where $C,\varkappa>0$ are constants that do not depend on $n$ and $\gamma.$
\end{lem}
\begin{proof}
The expression
$\sum_{p=1}^q \partial_{y_1}^K f(X_p^x)$
can be viewed as a deterministic function of
$x,Z_1,Z_{2},\ldots,Z_q$
$$
\sum_{p=1}^q  \partial_{y_1}^K f(X_p^x)
=F(x,Z_1,Z_{2},\ldots,Z_q).
$$
By the (conditional) Gaussian Poincar\'e inequality,
we have
$$
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]
\le\mathsf E_x\left[
\|\nabla_Z F(x,Z_1,Z_{2},\ldots,Z_q)\|^2
\right],
$$
where $\nabla_Z F=(\partial_{Z_1} F,\ldots,\partial_{Z_q} F)$,
and $\|\cdot\|$ denotes the Euclidean norm.
Notice that \(\partial_{Z_j} F=\sqrt{\gamma}\,\partial_{y_j} F\) and
hence
$$
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]\leq\gamma^2\sum_{j=1}^{q}\mathsf{E}\left[\left(\sum_{p=1}^{q}\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right)^{2}\right].
$$
It is straightforward to check that
$\partial_{y_j}\partial_{y_1}^K f(X_p^x)=0$
whenever $p<j$. Therefore, we get
\begin{equation}\label{eq:10062018a2}
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]\leq\gamma^2\sum_{j=1}^{q}\mathsf{E}\left[\left(\sum_{p=j}^{q}\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right)^{2}\right].
\end{equation}
Now fix $p$ and $j$, $p\ge j$, in $\{1,\ldots,q\}$.
By Fa\`a di Bruno's formula
\[
\partial_{y_{1}}^{K}f\left(X_{p}^x\right)=\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X_{p}^x)\prod_{k=1}^{K}\left(\frac{\partial_{y_{1}}^{k}X^x_{p}}{k!}\right)^{m_{k}},
\]
where the sum is taken over all $K$-tuples of nonnegative integers
$(m_1,\ldots,m_K)$ satisfying
$$
1\cdot m_{1}+2\cdot m_{2}+\ldots+K\cdot m_{K}=K.
$$
Then
\begin{eqnarray*}
\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)
&=&\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K}+1)}(X^x_{p})\left[\partial_{y_{j}}X^x_{p}\right]\prod_{k=1}^{K}\left(\frac{\partial_{y_{1}}^{k}X_{p}^x}{k!}\right)^{m_{k}} \\
&&+\sum\frac{K!}{m_{1}!\ldots m_{K}!}f^{(m_{1}+\ldots+m_{K})}(X^x_{p})
\sum_{s=1}^{K}\frac{m_{s}}{s!}
\left(\frac{\partial_{y_{1}}^{s}X^x_{p}}{s!}\right)^{m_{s}-1}
\\
&& \times\left[\partial_{y_{j}}\partial_{y_{1}}^{s}X^x_{p}\right]
\prod_{k\le K,\,k\neq s}\left(\frac{\partial_{y_{1}}^{k}X^x_{p}}{k!}\right)^{m_{k}}.
\end{eqnarray*}
Using the bounds of
Lemmas \ref{lem:06062018a2} and~\ref{lem:06062018a3},
we obtain
\begin{eqnarray}
\label{eq:part-part}
\left|\partial_{y_{j}}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right|
\leq A_{K}\prod_{k=2}^{p}\alpha_{k}
\end{eqnarray}
with a suitable constant $A_{K}$.
Substituting this in~\eqref{eq:10062018a2},
we proceed as follows
\begin{align*}
\mathsf{Var}_x\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X_{p}^x\right)\right]
&\le
\gamma^2 A_{K}^{2}\sum_{j=1}^{q}
\mathsf{E}\left(\sum_{p=j}^{q}\prod_{k=2}^{p}\alpha_{k}\right)^{2}
\\
&\le
\frac{\gamma^2 A_{K}^{2}}{(1-\gamma B_\mu)^2}
\mathsf{E}\sum_{j=1}^{q}
\left(\sum_{p=j+1}^{q+1}  \prod_{k=2}^{p} \alpha_{k}
\right)^{2}
\\
%&=
%\frac{A_{K}^{2}}{(1-\gamma_1 b_\mu)^2}
%\sum_{j=l}^{q} \gamma_{j}
%\prod_{k=l+1}^{j} \alpha_{k}^2
%\left(
%\sum_{p=j+1}^{q+1} \gamma_{p} \prod_{k=j+1}^{p} \alpha_{k}
%\right)^{2}
%\\
&\le
\frac{\gamma^2 A_{K}^{2}}{(1-\gamma B_\mu)^3}
\mathsf{E}\sum_{j=1}^{q}
\prod_{k=1}^{j} \alpha_{k}
\left(\sum_{p=j+1}^{q+1}  \prod_{k=j+1}^{p} \alpha_{k}
\right)^{2}
\end{align*}

Now, from the H\"older inequality, we obtain (with $\|X\|_p = (\mathsf{E}X^p)^{\frac{1}{p}}$)
\begin{align*}
\mathsf{E}\left[\sum_{j=1}^{q}\prod_{k=l}^{j}\alpha_{k}\left( \sum_{p=j+1}^{q+1}\prod_{k=j+1}^{p}\alpha_{k}\right)^{2}\right] & \leq\sum_{j=1}^{q}\left\Vert \prod_{k=1}^{j}\alpha_{k}\right\Vert _{2}\left\Vert \sum_{p=j+1}^{q+1} \prod_{k=j+1}^{p}\alpha_{k}\right\Vert _{4}^{2}\\
 & \leq\sum_{j=1}^{q} \left\Vert \prod_{k=1}^{j}\alpha_{k}\right\Vert _{2}\left(\sum_{p=j+1}^{q+1}\left\Vert \prod_{k=j+1}^{p}\alpha_{k}\right\Vert _{4}\right)^{2}.
\end{align*}
Now using the fact that $\prod\limits_{k=j+1}^{p}\alpha_{k} \leq \exp\left(-\sum\limits_{k=j+1}^{p}\gamma\mu'(X_{k-1}^x)\right),$
we get
\[
\mathsf{E}\left[\sum_{j=1}^{q}\prod_{k=1}^{j}\alpha_{k}\left(\sum_{p=j+1}^{q+1}\prod_{k=j+1}^{p}\alpha_{k}\right)^{2}\right]\leq\sum_{j=1}^{q} \zeta^{1/2}_{1,j}(2) \left(\sum_{p=j+1}^{q+1} \zeta^{1/4}_{j+1,p}(4)\right)^{2},
\]
where we denote
\[
\zeta_{l,j}(u)=\mathsf{E}\left[\rme^{-u\gamma\sum_{k=l}^{j}\mu'(X^x_{k-1})}\right],\quad u>0.
\]
Note that $\mu^{\prime}(x)$ is bounded due  our assumptions and from Theorem~1 in \cite{delyon1999small} and Lemma~\ref{lem:v_ergodicity} in Appendix~\ref{sec:appendix} it follows that
\[
\mathsf{E}\left[\rme^{-u\gamma\left(\sum_{k=l}^{j}[\mu'(X^x_{k-1})-\pi_\gamma(\mu')]\right)}\right]\leq C_1 \rme^{\varkappa n\gamma^2}(1+V(x)),\quad u\gamma\leq \gamma_0,
\]
for some constants $\gamma_0$ and $C_1,\varkappa>0$. Then we have
\[
\zeta_{l,j}(u)=\mathsf{E}\left[\rme^{-s\gamma\sum_{k=l}^{j}\mu'(X^x_{k-1})}\right]\leq  C_1 \rme^{\varkappa n\gamma^2}(1+V(x)) \rme^{-s\gamma (j-l+1)\pi_\gamma(\mu')}.
\]
Furthermore, since $\mu\pi',\mu'\pi\in L^{1}(\mathbb{R})$ and $\pi^{\prime}(x) = -\frac{1}{2}\pi(x)\mu(x)$, we have
\[
\pi(\mu')=\int\mu'(x)\pi(x)\,dx=-\int\mu(x)\pi'(x)\,dx=\frac{1}{2}\int\mu^{2}(x)\pi(x)\,dx>0
\]
Note also that \(\pi_\gamma(\mu^{\prime}) \geq \pi_\gamma(\mu^{\prime}) - C_2\sqrt{\gamma}\)
yielding the bound
\[
\zeta_{l,j}(s) \leq  C_1 \rme^{\varkappa n\gamma^2}(1+V(x)) \rme^{-s\gamma(j-l+1)\alpha}
\]
where $ \alpha = \frac{1}{2}\int \mu^2(x)\pi(x)\,dx - C_1\sqrt{\gamma} > 0$ for sufficiently small $\gamma$. Hence we obtain
\begin{align*}
\sum_{p=j+1}^{q+1} \zeta^{1/4}_{j+1,p}(4) &\leq (C_1 \rme^{\varkappa n\gamma^2}(1+V(x)))^{1/4}\sum_{p=j+1}^{q+1} \rme^{-\gamma(p-j)\alpha}
\\
&\leq  (C_1 \rme^{\varkappa n\gamma^2}(1+V(x)))^{1/4}\frac{1}{1- \rme^{- \gamma\alpha}}
\end{align*}
and
\begin{align*}
\sum_{j=1}^{q} \zeta^{1/2}_{1,j}(2) \leq (C_1 \rme^{\varkappa n\gamma^2}(1+V(x)))^{1/2}\sum_{j=0}^{q} \rme^{-\gamma j\alpha}
\\
\leq  (C_1 \rme^{\varkappa n\gamma^2}(1+V(x)))^{1/2}\frac{ 1}{1- \rme^{- \gamma\alpha}}.
\end{align*}
Thus the final bound follows:
\begin{align*}
\mathsf{Var}\left[\sum_{p=1}^{q}\partial_{y_{1}}^{K}f\left(X^x_{p}\right)\right] \leq \gamma^{-1} C_K \rme^{\varkappa n\gamma^2} (1+V(x))
\end{align*}
 with $C_K$  depending neither on $q$ nor on $\gamma$. The proof is completed.
\end{proof}

@@

\begin{lem}
\label{lem:drift}
 Assume that {\bf (H1)} and {\bf (H2)} and without loss of generality consider $\nabla U(0) = 0$. 
 Then the kernel $Q_\gamma$ from \eqref{eq:ula_kernel} satisfies drift condition \eqref{eq:lyapunov} for any $0 < \gamma < \overline{\gamma} = \frac{m}{4L}$ with drift function $V(x) = 1 + \|x\|^2$,   $\lambda = \exp{\left(-\frac{m}{2}\right)}$, $C = \frac{25K_2^2}{8} + d + m$ with $K_2$ from \eqref{eq:H3}, $m$ from {\bf (H2)}.
\end{lem}

@@

\begin{lem}
\label{lem:v_ergodicity}
 Assume  {\bf (H1)} and {\bf (H2)}. Then for $0 < \gamma < \overline{\gamma}=m / 4L^2$, for any $x \in \rset^d$ it holds
$$
d_V(\delta_xQ_{\gamma}^{1,n},\pi_\gamma) \leq C\rho^n\left(V(x) + \pi_\gamma(V)\right)
$$
with $V(x) = 1 + \|x\|^2$ and constants
$$
C = \left(1 + \exp{\left(-\frac{m\gamma}{2}\right)}\right)\left(1+\frac{\overline{b}}{(1-\varepsilon)(1-\exp{\left(-\frac{m\gamma}{2}\right)} - \frac{2b}{1+d})}\right);
$$
